Electronic polarizability as the fundamental variable in the dielectric properties of two-dimensional materials

### 2019-10-04 paper.tex
ADd more scripts

The dielectric constant $\varepsilon$ (also known as the relative permittivity) 
plays a crucial role in bridging various fundamental material
properties, such as bandgaps\cite{Moss_1950_relation,Moss_1985_n_Eg}, 
optical absorption\cite{kittel_2005_introduction} and 
conductivities\cite{Dressel_2001_electrodynamics}   
with elemental interactions. 
The central place of $\varepsilon$ in solid-state physics drives the analysis of several phenomena 
where is common to classify a material accordingly to its ability to screen an 
electric field $\boldsymbol{E}$ in terms of insulators, metals and semiconductors. Such definitions determine a broad range of 
condensed matter physics, as well as in related fields in chemistry and materials science. 
The ability to compute and measure $\varepsilon$ in bulk materials is well established via different 
theoretical \cite{Adler_1962,Hybertsen_1987} and experimental techniques \cite{palik_1998handbook} of distinct flavors
% where the probe of the dielectric properties 
% is made through an external electric field. 
%
Despite its obvious appeal, however, it is still unknown whether such quantity can determine the 
% electronic and
dielectric properties of two-dimensional (2D) materials \cite{Novoselov_2016}.  
%
The confined nature of such atomically-thin 2D crystals associated
with the attenuated and anisotropic character of the dielectric
screening
\cite{Keldysh_1979_eps_multi,Sharma_1985,Low_2014_screening_BP,Cudazzo_2011_screening_2D,Bechstedt_2012,Cudazzo_2010_screen2D,Nazarov_2015_2D_3D}
have generated long-standing debates whether the dielectric constant
truly represents dielectric features of such low-dimensional systems,
% or it can be used only as an
% additional parameter from the bulk-counterparts.
The controversy of
$\varepsilon$ values reported by both theoretical and experimental
approaches can be widely seen throughput literature\cite{Li_2016},
where the variation of $\varepsilon$ can be more than one order of
magnitude. As a consequence, several key physical parameters that
scales with $\varepsilon$, such as the exciton binding energy and
Debye screening length, cannot be reliably estimated due to the
discrepancy of reported $\varepsilon$ values. In this letter, we give
a thorough study of the underlying issue. Using \textbf{ab initio}
simulations of a model system, we demonstrate that the macroscopic
dielectric constant strongly depends on the size of the superlattice,
making it unsuitable to describe the screening of a 2D material. On
the contrary, by analyzing the formalism of dielectric tensors, we
propose that the electronic polarizability is the true descriptor
which uniquely captures the dielectric nature of 2D materials. The 2D
electronic polarizability has unique definition, which overcomes the
disadvantage of ambiguity compared with the conventionally used
effective dielectric medium model for 2D materials. Moreover, we show
the universal scaling relations for in- and out-of-plane 2D electronic
polarizabilities with the electronic and geometric information of the
2D material. The concept of electronic polarizabilities bridges the
gap between the dielectric properties of 2D and 3D systems, and can be
extended to characterize the dielectric anisotropy for any material
dimensions.

@@

absorption and electron energy loss spectrum (EELS, equivalent to $1 / \mathrm{Im}(\varepsilon(\omega))$), suffers the same

@@

%
%
Using these relations, we show the calculated
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
of the selected TMDCs as a function of $L$ in the bottom panels of
Figure \ref{fig-1}b and \ref{fig-1}c, respectively.  In contrast to
$\varepsilon_{\mathrm{SL}}^{\parallel}$ and
$\varepsilon_{\mathrm{SL}}^{\perp}$, We observe that both
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
reach convergence when $L$ exceeds 10 \AA and 15 \AA, respectively.
{\color{red} Convergence plot in SI} Such result is in good agreement
with the spatially localized induced dipole moment of a 2D materials
as shown in Supplementary Figure~\ref{SI-fig:rho-profile}. 
%
%
Interestingly, we can use Eqs.\ref{eq:alpha-para-def} and
\ref{eq:alpha-perp-def} to reproduce the trends noticed in the top
panels in Figure\ref{fig-1}{\textbf b} and \ref{fig-1}{\textbf c} for
$\varepsilon_{\mathrm{SL}}^{\parallel}$ and
$\varepsilon_{\mathrm{SL}}^{\perp}$ as a function of $L$ around a
centered magnitude of $\alpha_{\mathrm{2D}}^{\parallel}$ and
$\alpha_{\mathrm{2D}}^{\perp}$
(Figure \ref{fig-1}\textbf{d}-\textbf{e}).
% A similar curve profile is obtained in both components of the dielectric constant including the much 
% abrupt variation of $\varepsilon_{\mathrm{SL}}^{\perp}$ with $L$ which is due to 
% interlayer interactions.
%\todo[inline]{The original claim of this sentence, that $\varepsilon_{\mathrm{SL}}^{\perp}$ varies more due to interlayer interactions is not 100\% true. I think it is better not to explicitly mention this.}
Such relations can also be used to remove the dependence on $L$ for
frequency-dependent $\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$
and $\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$, generating
lattice-independent electronic polarizability
$\alpha^{\parallel}_{\mathrm{SL}}(\omega)$ and
$\alpha^{\perp}_{\mathrm{SL}}(\omega)$ in the frequency domain,
respectively (details see Supplementary Section \ref{SI-ssec:gw}).
%
% 
% 
% 
% 
These findings indicate that the electronic polarizability $\alpha_{\mathrm{2D}}$ captures the essence
of the dielectric properties of 2D materials. In contrast to the ill-defined macroscopic $\varepsilon_{\mathrm{SL}}$, $\alpha_{\mathrm{2D}}$ has unique definition, and does not suffer from the dependency on the lattice size.
More discussions about the choice of the
2D polarizability, comparison with other methods, simulations at the
frequency-dependent domain can be found in Supplementary Section
\ref{SI-ssec:gw}.

>>>>

The dielectric constant $\varepsilon$ (also known as the relative permittivity) 
plays a crucial role in bridging various fundamental material
properties, such as bandgaps\cite{Moss_1950_relation,Moss_1985_n_Eg}, 
optical absorption\cite{kittel_2005_introduction} and 
conductivities\cite{Dressel_2001_electrodynamics}   
with elemental interactions. 
The central place of $\varepsilon$ in solid-state physics drives the analysis of several phenomena 
where is common to classify a material accordingly to its ability to screen an 
electric field $\boldsymbol{E}$ in terms of insulators, metals and semiconductors. Such definitions determine a broad range of 
condensed matter physics, as well as in related fields in chemistry and materials science. 
The ability to compute and measure $\varepsilon$ in bulk materials is well established via different 
theoretical \cite{Adler_1962,Hybertsen_1987} and experimental techniques \cite{palik_1998handbook} of distinct flavors
% where the probe of the dielectric properties 
% is made through an external electric field. 
%
Despite its obvious appeal, however, it is still unknown whether such quantity can determine the 
% electronic and
dielectric properties of two-dimensional (2D) materials \cite{Novoselov_2016}.  
%
The confined nature of such atomically-thin 2D crystals associated
with the attenuated and anisotropic character of the dielectric
screening
\cite{Keldysh_1979_eps_multi,Sharma_1985,Low_2014_screening_BP,Cudazzo_2011_screening_2D,Bechstedt_2012,Cudazzo_2010_screen2D,Nazarov_2015_2D_3D}
have generated long-standing debates whether the dielectric constant
truly represents dielectric features of such low-dimensional systems,
% or it can be used only as an
% additional parameter from the bulk-counterparts.
The controversy of
$\varepsilon$ values reported by both theoretical and experimental
approaches can be widely seen throughput literature\cite{Li_2016},
where the variation of $\varepsilon$ can be more than one order of
magnitude. As a consequence, several key physical parameters that
scales with $\varepsilon$, such as the exciton binding energy and
Debye screening length, cannot be reliably estimated due to the
discrepancy of reported $\varepsilon$ values. In this letter, we give
a thorough study of the underlying issue. Using \textit{ab initio}
simulations of a model system, we demonstrate that the macroscopic
dielectric constant strongly depends on the size of the superlattice,
making it unsuitable to describe the screening of a 2D material. On
the contrary, by analyzing the formalism of dielectric tensors, we
propose that the electronic polarizability is the true descriptor
which uniquely captures the dielectric nature of 2D materials. The 2D
electronic polarizability has unique definition, which overcomes the
disadvantage of ambiguity compared with the conventionally used
effective dielectric medium model for 2D materials. Moreover, we show
the universal scaling relations for in- and out-of-plane 2D electronic
polarizabilities with the electronic and geometric information of the
2D material. The concept of electronic polarizabilities bridges the
gap between the dielectric properties of 2D and 3D systems, and can be
extended to characterize the dielectric anisotropy for any material
dimensions.

@@

absorption (abs., equivalent to $\mathrm{Im}(\varepsilon_{\mathrm{SL}}(\omega))$), refractive index ($n$,  $\sim{}\sqrt{\mathrm{Re}(\varepsilon_{\mathrm{SL}})}$) and electron energy loss spectrum (EELS, equivalent to $-1 / \mathrm{Im}(\varepsilon_{\mathrm{SL}}(\omega))$), suffers the same

@@

%
%
Using these relations, we show the calculated
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
of the selected TMDCs as a function of $L$ in the bottom panels of
Figure \ref{fig-1}b and \ref{fig-1}c, respectively.  In contrast to
$\varepsilon_{\mathrm{SL}}^{\parallel}$ and
$\varepsilon_{\mathrm{SL}}^{\perp}$, We observe that both
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
reach convergence when $L$ exceeds 10 \AA and 15 \AA,
respectively. Such result is in good agreement with the spatially
localized induced dipole moment of a 2D materials as shown in
Supplementary Figure~\ref{SI-fig:rho-profile}.
%
%
Interestingly, we can use Eqs.\ref{eq:alpha-para-def} and
\ref{eq:alpha-perp-def} to reproduce the trends noticed in the top
panels in Figure\ref{fig-1}{\textbf b} and \ref{fig-1}{\textbf c} for
$\varepsilon_{\mathrm{SL}}^{\parallel}$ and
$\varepsilon_{\mathrm{SL}}^{\perp}$ as a function of $L$ around a
centered magnitude of $\alpha_{\mathrm{2D}}^{\parallel}$ and
$\alpha_{\mathrm{2D}}^{\perp}$
(Figure \ref{fig-1}\textbf{d}-\textbf{e}).
% A similar curve profile is obtained in both components of the dielectric constant including the much 
% abrupt variation of $\varepsilon_{\mathrm{SL}}^{\perp}$ with $L$ which is due to 
% interlayer interactions.
%\todo[inline]{The original claim of this sentence, that $\varepsilon_{\mathrm{SL}}^{\perp}$ varies more due to interlayer interactions is not 100\% true. I think it is better not to explicitly mention this.}
Such relations can also be used to remove the dependence on $L$ for
frequency-dependent $\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$
and $\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$, generating
lattice-independent electronic polarizability
$\alpha^{\parallel}_{\mathrm{SL}}(\omega)$ and
$\alpha^{\perp}_{\mathrm{SL}}(\omega)$ in the frequency domain,
respectively (details see Supplementary Section \ref{SI-ssec:gw}).
%
% 
% 
% 
% 
These findings indicate that the electronic polarizability $\alpha_{\mathrm{2D}}$ captures the essence
of the dielectric properties of 2D materials. In contrast to the ill-defined macroscopic $\varepsilon_{\mathrm{SL}}$, $\alpha_{\mathrm{2D}}$ has unique definition, and does not suffer from the dependency on the lattice size.
More discussions about the choice of the
2D polarizability, comparison with other methods, simulations at the
frequency-dependent domain can be found in Supplementary Section
\ref{SI-ssec:gw}.
